---
title: "p8105_hw6_zz3168"
author: "Zixuan Zhang"
date: "2023-11-28"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal())

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


### Problem 1

In the data cleaning code below we create a `city_state` variable, change `victim_age` to numeric, modifiy victim_race to have categories white and non-white, with white as the reference category, and create a `resolution` variable indicating whether the homicide is solved. 

```{r q1_data_cleaning}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) |> 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) |> 
  filter(victim_race %in% c("White", "Black")) |> 
  filter(!(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) |> 
  select(city_state, resolution, victim_age, victim_sex, victim_race)
```

Next we fit a logistic regression model using only data from Baltimore, MD. We model `resolved` as the outcome and `victim_age`, `victim_sex`, and `victim_race` as predictors. We save the output as `baltimore_glm` so that we can apply `broom::tidy` to this object and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims.

```{r q1_glm_baltimore}
baltimore_glm = 
  filter(homicide_df, city_state == "Baltimore, MD") |> 
  glm(resolution ~ victim_age + victim_sex + victim_race, family = binomial(), data = _)

baltimore_glm |> 
  broom::tidy() |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(OR, OR_CI_lower, OR_CI_upper) |>
  knitr::kable(digits = 3)
```

Below, by incorporating `nest()`, `map()`, and `unnest()` into the preceding Baltimore-specific code, we fit a model for each of the cities, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. We show the first 5 rows of the resulting dataframe of model results.

```{r q1_glm_all_cities}
model_results = 
  homicide_df |> 
  nest(data = -city_state) |> 
  mutate(
    models = map(data, \(df) glm(resolution ~ victim_age + victim_sex + victim_race, 
                             family = binomial(), data = df)),
    tidy_models = map(models, broom::tidy)) |> 
  select(-models, -data) |> 
  unnest(cols = tidy_models) |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(city_state, OR, OR_CI_lower, OR_CI_upper)

model_results |>
  slice(1:5) |> 
  knitr::kable(digits = 3)
```

Below we generate a plot of the estimated ORs and CIs for each city, ordered by magnitude of the OR from smallest to largest. From this plot we see that most cities have odds ratios that are smaller than 1, suggesting that crimes with male victims have smaller odds of resolution compared to crimes with female victims after adjusting for victim age and race. This disparity is strongest in New yrok. In roughly half of these cities, confidence intervals are narrow and do not contain 1, suggesting a significant difference in resolution rates by sex after adjustment for victim age and race. 

```{r q1_plot}
model_results |> 
  mutate(city_state = fct_reorder(city_state, OR)) |> 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

do the r regression

```{r}
boost_sample_r = 
  weather_df |> 
  bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  janitor::clean_names()

conf_r =
  boost_sample_r |> 
  summarize(
    c_lower = quantile(r_squared, 0.025),
    c_upper = quantile(r_squared, 0.975)
  ) |> 
    knitr::kable()
  
  

```


#Identify the 2.5% and 97.5% quantiles 
```{r}
boost_sample_b = 
  weather_df |> 
  bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results = map(models, broom::tidy)
  ) |> 
  select(-strap, -models) |> 
  unnest(results) |>
  select(id = `.id`, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  janitor::clean_names() |> 
  rename(beta0 = intercept, beta1 = tmin, beta2 = prcp) |> 
  mutate(
    log_b1 = log(beta0 * beta1),
    log_b2 = log(beta1 * beta2)
  )


conf_beta0 = 
  boost_sample_b |> 
  summarize(
    c_lower = quantile(log_b1, 0.025),
    c_upper = quantile(log_b1, 0.975)
  ) |> 
 knitr::kable() 


conf_beta1 = 
  boost_sample_b |> 
  summarize(
    c_lower = quantile(log_b2, 0.025,na.rm = TRUE),
    c_upper = quantile(log_b2, 0.975,na.rm = TRUE)
  ) |> 
 knitr::kable() 

  
  
```

According to the result, The 2.5% and 97.5% quantiles of of log(beta 1*beta 2) is -8.86 and -4.60. The 2.5% and 97.5% quantiles of R squard is 0.89 and 0.94. 

# do the r plot

```{r}
boost_sample_r |> 
  ggplot(aes(x = r_squared)) +
  geom_density()+
  labs(
    title = "Estimated R-Squared's Distribution ",
    x = "Estimated R Squared",
    y = "Density"
  )

```

#do the plot for Beta
```{r}
boost_sample_b |> 
  select(log_b2) |> 
  ggplot(aes(x = log_b2)) + 
  geom_density() + 
  labs(
    title = "Estimated Beta Distribution",
    x = "Estimated Beta1 * Beta2",
    y = "Density"
  )

```
According to the plot , we could see that the plot for R suqard is approximately normal, and the plot for  log(beta 1*beta 2) is skewed to the left.

 
### Problem 3

##clean and tidy the data
```{r}
birthwt_df = 
  read_csv("./data/birthweight.csv") |> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform)
  ) |> 
  janitor::clean_names()


  
```

##build a regression model for birthweight.
```{r}
model_fit =
  lm(bwt ~ babysex + bhead + blength + mrace + smoken, data = birthwt_df) 

```
My model is based on factors that underlie birth weight. and consider the baby’s head circumference at birth,  baby’s length at birth, and mother’s race will influence the babay's birth weight, so i use these data for delivery in years and average number of cigarettes smoked per day during pregnancy for predictors.

##plot of Model Residuals
```{r}
plot_df = 
birthwt_df |> 
  select(bwt, babysex, bhead, blength, mrace, smoken) |> 
  add_residuals(model_fit) |> 
  add_predictions(model_fit) |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_violin() 
  
```

## the other model 
```{r}
model_2 = 
  lm(bwt ~ blength + gaweeks, data = birthwt_df) |> 
  broom::tidy()

model_3 = 
  lm(bwt ~ bhead* babysex + blength* babysex + bhead* blength* babysex, data = birthwt_df) |> 
   broom::tidy()

```

##compare the model
```{r}
cv_df = 
  crossv_mc(birthwt_df, 100) |>
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) |> 
  mutate(
    model_1 = map(train, \(df) lm(bwt ~ babysex + bhead + blength + mrace + smoken, data = df)),
    model_2 = map(train, \(df) lm(bwt ~ blength + gaweeks, data = df)),
    model_3 = map(train, \(df) lm(bwt ~ bhead* babysex + blength* babysex + bhead* blength* babysex, data = df))
  ) |> 
   mutate(
    rmse_1 = map2_dbl(model_1, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_2 = map2_dbl(model_2, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_3 = map2_dbl(model_3, test, \(mod, df) rmse(model = mod, data = df)))
```


```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```
According to the plot we could saw that the model 2 has the highest values of rmse, and the model 1 have the lowest rmse.
